---
title: "Homework 6.4 (8th edition)"
author: "Duong Ngo"
date: "9/26/2019"
output: pdf_document
header-includes: 
    - \usepackage{amsmath}
---

```{r setup}
knitr::opts_knit$set(root.dir = 'C:/Users/The Asian Kid/Desktop/Math 411/R Data')
```

## Problem 6.4.2
a) Find point estimate of $\sigma$  
```{r}
a = read.table('E6_4-02.txt')
v642 = var(a)
sqrt(v642)
```
b) Find 95% confidence interval for $\sigma$  
```{r}
cbind(sqrt((9-1)*v642/qchisq(.975,(9-1))), sqrt((9-1)*v642/qchisq(.025,(9-1))))
```
c) Find 90% confidence interval for $\sigma$  
```{r}
cbind(sqrt((9-1)*v642/qchisq(.95,(9-1))), sqrt((9-1)*v642/qchisq(.05,(9-1))))
```

## Problem 6.4.3
a) Calculate the sample mean and sample variance for the data  
```{r}
b =  read.table('E6_4-03.txt')
v643 = var(b)
m643 = mean(b[,1])
v643
m643
```
b) The 90% confidence interval for $\sigma^2$ is:  
```{r}
cbind((25-1)*v643/qchisq(.95,(25-1)), (25-1)*v643/qchisq(.05,(25-1)))
```

c) The 90% confidence interval for $\sigma$ is:  
```{r}
cbind(sqrt((25-1)*v643/qchisq(.95,(25-1))), sqrt((25-1)*v643/qchisq(.05,(25-1))))
```
d) Consider the qqplot of the data:  
```{r}
qqplot(b[,1], rnorm(26))
```
Since the qqplot of the data form approximately a straightline, the assumption of normality is valid.  

## Problem 6.4.4
a) The 95% confidence interval of $\sigma^2$ is:  
```{r}
c = read.table('E6_4-04.txt')
cbind((10-1)*var(c)/qchisq(.975,(10-1)), (10-1)*var(c)/qchisq(.025,(10-1)))
```
b) The 95% confidence interval of $\sigma$ is:
```{r}
cbind(sqrt((10-1)*var(c)/qchisq(.975,(10-1))), sqrt((10-1)*var(c)/qchisq(.025,(10-1))))
```

## Problem 6.4.10
a) The point estimate for $\sigma_x^2/\sigma_y^2$ is:  
```{r}
0.004/0.0076
```
b) The 95% confidence interval for $\sigma_x^2/\sigma_y^2$ is:  
```{r}
cbind(1/qf(.975, 10-1, 9-1)*0.004/0.0076, qf(.975, 9-1, 10-1)*0.004/0.0076)
```

## Problem 6.4.12
The 90% confidence interval for $\sigma_x^2/\sigma_y^2$ is:  '
```{r}
cbind(1/qf(.95, 16-1, 13-1)* 0.197^2/ 0.318^2, qf(.95, 13-1, 16-1)* 0.197^2/ 0.318^2)
```
Thus the 90% confidence interval for $\sigma_x/\sigma_y$ is:  
```{r}
cbind(sqrt(1/qf(.95, 16-1, 13-1)* 0.197^2/ 0.318^2), sqrt(qf(.95, 13-1, 16-1)* 0.197^2/ 0.318^2))
```

## Problem 6.4.13
a) The point estimate for $\sigma_x^2/\sigma_y^2$ is:  
```{r}
e = read.delim('E6_4-13.txt', header= FALSE)
var(e[,1], na.rm = TRUE)/var(e[,2], na.rm = TRUE)
```
b) The upper bound for the 95% confidence interval of $\sigma_x^2/\sigma_y^2$ is:
```{r}
qf(.95, 10-1, 8-1)*var(e[,1], na.rm = TRUE)/var(e[,2], na.rm = TRUE)
```

## Problem 6.4.14
a) The 95% confidence interval for $\sigma_x^2/\sigma_y^2$ is:
```{r}
f = read.table('E6_4-14.txt')
cbind(1/qf(.975, 14-1, 14-1)* var(f[,1])/ var(f[,2]), qf(.975, 14-1, 14-1)* var(f[,1])/var(f[,2]))
```
b) The 95% confidence interval for $\sigma_x/\sigma_y$ is:  
```{r tidy= TRUE}
f = read.table('E6_4-14.txt')
cbind(sqrt(1/qf(.975, 14-1, 14-1)* var(f[,1])/ var(f[,2])), sqrt(qf(.975, 14-1, 14-1)* var(f[,1])/var(f[,2])))
```

