---
title: "HW 7.4"
author: "Duong Ngo"
date: "10/5/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 7.4.1
The sample size n needed here is:
```{r}
(qnorm(.975)^2*4.84/0.4^2)
```

Rounding up, the needed sample size is 117  

## Problem 7.4.2
The sample size n needed here is:
```{r}
(qnorm(.975)^2*169/1.5^2)
```
Rounding up, the needed sample size is 289

## Problem 7.4.3
a) The needed sample size is:
```{r}
(qnorm(.95)^2*0.02^2/0.001^2)
```
Rounding up, the needed sample size is 1083  
b) The 90% confidence interval of the mean is:
```{r}
c1 = cbind(6.048-qnorm(.95)*(0.022/sqrt(1219)),6.048+qnorm(.95)*(0.022/sqrt(1219)))
c1
```
c) The new estimated mean is:
```{r}
c=(c1[,1]+c1[,2])/2
c
```
Thus the estimated saving per year after the new adjustment is:
```{r}
14000*((6.09-c)/0.01)
```
d) Assume boxes weight is normally distributed with $\mu= 6.048$ and $\sigma = 0.022$. Hence:  
\begin{align*}
&P(X<6)=P(\frac{6-6.048}{0.022})\\
&P(X<6)=P(Z<-2.18)\\
&P(X<6)=1-\theta(2.18)\approx 0.0146
\end{align*}
Equivalently, 0.0146 of the boxes are less than 6 pounds.

## Problem 7.4.7
a) The needed sample to get 0.03 margin of error with 95% confidence is:
```{r}
ceiling(qnorm(.975)^2/(4*0.03^2))
```
b) The needed sample to get 0.02 margin of error with 95% confidence is:
```{r}
ceiling(qnorm(.975)^2/(4*0.02^2))
```
c) The needed sample to get 0.03 margin of error with 90% confidence is:
```{r}
ceiling(qnorm(.95)^2/(4*0.03^2))
```
## Problem 7.4.8
The needed sample size n is:
```{r}
p8 = 54/137
ceiling(qnorm(.95)^2*(p8-p8^2)/0.04^2)
```

## Problem 7.4.9
```{r}
p9 = 54/137
ceiling(qnorm(.95)^2*(p8-p8^2)/0.04^2)
```

## Problem 7.4.12
a) First we find m value from equation 7.4.2:
```{r}
m1 = ceiling(qnorm(.975)^2*(1/2-1/2^2)/0.04^2)
m1
```
Then substituing m1, we obtain the needed sample size n1 when the population size is 1500:
```{r}
n1 = ceiling(m1/(1+(m1-1)/1500))
n1
```
b) For the population size 15000, the needed sample size is:
```{r}
n2 = ceiling(m1/(1+(m1-1)/15000))
n2
```
c) For the population size 25000, the needed sample size is:
```{r}
n3 = ceiling(m1/(1+(m1-1)/25000))
n3
```
  
    
      
      
## Problem 7.4.14

