---
title: "Homework 7.3"
author: "Duong Ngo"
date: "9/29/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 7.3.1
a) The point estimate of p is:  
```{r}
ep1 = 24/642
24/642
```
b) The 95% confidence interval for p from equation 7.3.2 is:
```{r}
cbind(ep1-qnorm(0.975)*sqrt((ep1*(1-ep1))/624), ep1+qnorm(0.975)*sqrt((ep1*(1-ep1))/624))
```
c) The 95% confidence interval for p from equation 7.3.4 is: 
```{r}
n1 = qnorm(.975)
cbind((ep1+n1^2/(2*624)-n1*sqrt((ep1-ep1^2)/624+n1^2/(4*624^2)))/(1+(n1^2/624)),(ep1+n1^2/(2*624)+n1*sqrt((ep1-ep1^2)/624+n1^2/(4*624^2)))/(1+(n1^2/624)))
```      
d) The 95% confidence interval for p from equation 7.3.5 is:
```{r}
ep12 = (24+2)/(624+4)
cbind(ep12-qnorm(.975)*sqrt((ep12-ep12^2)/(624+4)),ep12+qnorm(.975)*sqrt((ep12-ep12^2)/(624+4)))
```

e) The one-sided confidence interval for p that provides an upper bound is:
```{r}
cbind(0,ep1+qnorm(.95)*sqrt((ep1-ep1^2)/624))
```

## Problem 7.3.2
a) Give a point estimate of p:
```{r}
ep2 = 142/200
```
b) Find 90% confidence interval for p using equation 7.3.2:
```{r}
cbind(ep2-qnorm(0.95)*sqrt((ep2*(1-ep2))/200), ep2+qnorm(0.95)*sqrt((ep2*(1-ep2))/200))
```
c) Find 90% confidence interval for p using equation 7.3.4
```{r}
n2 = qnorm(.95)
cbind((ep2+n2^2/(2*200)-n2*sqrt((ep2-ep2^2)/200+n2^2/(4*200^2)))/(1+(n2^2/200)),(ep2+n2^2/(2*200)+n2*sqrt((ep2-ep2^2)/200+n2^2/(4*200^2)))/(1+(n2^2/200)))
```
d) Find 90% confidence interval for p using equation 7.3.5
```{r}
ep22 = (142+2)/(200+4)
cbind(ep22-qnorm(.95)*sqrt((ep22-ep22^2)/(200+4)),ep22+qnorm(.95)*sqrt((ep22-ep22^2)/(200+4)))
```
e) The one-sided confidence interval for p that provides a lower bound is:
```{r}
cbind(ep2-qnorm(0.9)*sqrt((ep2-ep2^2)/200),1)
```

## Problem 7.3.5
a) Give a point estimate for p:
```{r}
ep3 = 9/50
```
b) Find 90% confidence interval for p using equation 7.3.2:
```{r}
cbind(ep3-qnorm(0.975)*sqrt((ep3*(1-ep3))/50), ep3+qnorm(0.975)*sqrt((ep3*(1-ep3))/50))
```
c) Find 90% confidence interval for p using equation 7.3.4
```{r}
n3 = qnorm(.975)
cbind((ep3+n3^2/(2*50)-n3*sqrt((ep3-ep3^2)/50+n3^2/(4*50^2)))/(1+(n3^2/50)),(ep3+n3^2/(2*50)+n3*sqrt((ep3-ep3^2)/50+n3^2/(4*50^2)))/(1+(n3^2/50)))
```
d) Find 90% confidence interval for p using equation 7.3.5
```{r}
ep32 = (9+2)/(50+4)
cbind(ep32-qnorm(.975)*sqrt((ep32-ep32^2)/(50+4)),ep32+qnorm(.975)*sqrt((ep32-ep32^2)/(50+4)))
```

## Problem 7.3.7
The 90% confidence interval for p1-p2 is:
```{r}
p1 = 840/2100
p2 = 323/1900
cbind(p1-p2-qnorm(.95)*sqrt((p1-p1^2)/2100+(p2-p2^2)/1900),p1-p2+qnorm(.95)*sqrt((p1-p1^2)/2100+(p2-p2^2)/1900))
```
## Problem 7.3.10
a) Give a point estimate of p1:
```{r}
ep101 = 28/194
```
b) Give the endpoints for the 95% confidence interval for p1:
```{r}
cbind(ep101-qnorm(0.975)*sqrt((ep101*(1-ep101))/194), ep101+qnorm(0.975)*sqrt((ep101*(1-ep3))/194))
```
c) Give the point estimate for p1-p2
```{r}
ep102 = 28/194 - 11/162
```
d) Find 95% confidence interval that gives lower bound for p1 - p2
```{r}
p11 = 28/194
p12 = 11/162
cbind(ep102-qnorm(0.95)*sqrt((p11-p11^2)/194+(p12-p12^2)/162),1)
```
123  123
