---
title: "HW 7.4 (8th edition)"
author: "Duong Ngo"
date: "10/25/2019"
output: pdf_document
---
## Problem 7.4.1
a) The critical region is:
```{r}
qchisq(.05, df=10)
```
Thus, we reject $H_0$ if $t\leq 3.940299$
b) The value of the test statistic is:
```{r}
a = read.csv("C:/Users/The Asian Kid/Desktop/Math 411/R Data/E7_4-01.txt", sep="")
v1 = var(a[,1])
(10*v1)/(525^2)
```

Since the value of the test statistic is outside the critical region, we cannot reject $H_0$  
c) The p-value is:
```{r}
pchisq(4.103709, df =10)
```

## Problem 7.4.3
a) The critical region is:
```{r}
qchisq(.95, df=24)
```
Thus, we reject $H_0$ if $t\leq 36.41503$
b) The value of the test statistic for the given sample is:
```{r}
b = read.csv("C:/Users/The Asian Kid/Desktop/Math 411/R Data/E7_4-03.txt", sep="")
v2 = var(b[,1])
(24*v2)/(140^2)
```

Since the value of the test statistic is outside the critical region, we cannot reject $H_0$ and conclude that the variance differs

## Problem 7.4.8
The value of the test statistic is:
```{r}
9.88/4.08
```
The value of the critical region is:
```{r}
qf(0.95, 12, 8)
```
Since the value of the test statistic is within the critical region, we cannot reject $H_0$, thus the ratio of variance of both variable is like to equal 1

## Problem 7.4.10
The value of the test statistic is:
```{r}
9201/4856
```
The value of the critical region is:
```{r}
qf(0.95, 6, 9)
```
Since the value of the test statistic is within the critical region, we cannot reject $H_0$, thus the ratio of variance of both variable is like to equals 1
