---
title: "HW82"
author: "Duong Ngo"
date: "10/22/2019"
output: pdf_document
---

In the coming problems, we would refer to the following formula:  
(1) T test for underlying normal distribution with common (unknown) variance  
$T = \frac{\bar{X}-\bar{Y}}{S_p\sqrt{1/n+1/m}}$ where $S_p = \sqrt{\frac{(n-1)S^2_x+(m-1)S^2_y}{n+m-2}}$  
(2) T test for underlying normal distribution with known (different) variance $\sigma^2_x$ and $\sigma^2_y$  
$Z = \frac{\bar{X}-\bar{Y}}{\sqrt{\frac{\sigma^2_x}{n}+\frac{\sigma^2_y}{m}}}$  
(3) T test for underlying normal distribution with unknown variance, sample size both $\geq 30$
$Z = \frac{\bar{X}-\bar{Y}}{\sqrt{\frac{S^2_x}{n}+\frac{S^2_y}{m}}}$  

## Problem 8.2.1
a) According to table 8.2.1, the critical region value is:  
```{r}
qt(0.05, 10+10-2)
```
The critical region is thus:  
```{r, out.width="300px", out.height="300px"}
xseq=seq(-4,4,.01)
densities=dnorm(xseq, 0,1)
plot(xseq, densities,xlab="", ylab="Density", type="l", main="PDF of Standard Normal")
```
b)
```{r}
a = read.delim('8_2-01.txt', header = FALSE)
t.test(a[,1],a[,2], alternative = "less", conf.level =0.95)
```
Since $p<0.5$, we reject the null hypothesis $H_0$
c)
```{r}
ap = data.frame(a[,1], a[,2])
boxplot(ap)
```
From the boxplot, we can confirm the hypothesis that $\mu_x<\mu_y$

## Problem 8.2.2
a) Since we assume the variance is equal, the test statistic is computed using equation (1):  
$T = \frac{\bar{X}-\bar{Y}}{S_p\sqrt{27}}$ where $S_p = \sqrt{\frac{15S^2_x+12S^2_y}{27}}$   
According to table 8.2.1, the critical region value for $\alpha= 0.01$ is:
```{r}
-qt(0.01, 27)
```
i.e: t$\geq 2.47266$  
b) With the given values, the value of the test statistic is:
```{r}
(415.16-347.4)/sqrt((15*1356.75+12*692.21)/27*(1/16+1/13))
```
Since the value of the test statistic is within the critical region, we reject $H_0$ and conclude $\mu_x>\mu_y$
c) Using Welsch t-test, first we find the approximate degree of freedom needed:
```{r}
floor((1356.75/16+692.21/13)^2/(((1356.75/16)^2)/15+((692.21/13)^2)/12))
```
Thus, using table 8.2.1, the critical region value for $\alpha= 0.01$ is:
```{r}
-qt(0.01, 26)
```
i.e: t$\geq 2.47863$  
The value of the test statistic is:
```{r}
(415.16-347.4)/sqrt(1356.75/16+692.21/13)
```
Since the value of the test statistic is still within the critical region, we reject $H_0$ and conclude $\mu_x>\mu_y$  

## Problem 8.2.12
a) The critical region value for $\alpha = 0.025$ for one-sided alternative hypothesis is:
```{r}
-qnorm(0.975)
```
i.e: $z\leq -1.959964$
b) Hypothesis testing using R:
```{r}
b = read.table('7_2-05.txt')
t.test(b[,1],b[,2], alternative = "less", conf.level = 0.975)
```
Since the p-value is less than $\alpha$, we reject $H_0$ at 2.5% signifcance level.  
c) Box-whisker plot:
```{r}
bp = data.frame(b[,1], b[,2])
boxplot(bp)
```
From the boxplot, we can confirm the hypothesis that $\mu_x<\mu_y$


