---
title: "HW 8.3"
author: "Duong Ngo"
date: "10/25/2019"
output: pdf_document
---
## Problem 8.3.1
a) The significance level $\alpha$ error of the test is:
```{r}
pbinom(6, 100, 0.08)
```
b) The significance level $\beta$ error of the test is:
```{r}
1-pbinom(6, 100, 0.04)
```

## Problem 8.3.3
a)
```{r}
1 - pbinom(151, 192, 0.75)
```
b)
```{r}
pbinom(151, 192, 0.8)
```

## Problem 8.3.6
The value of our test statistic for proportion here is
```{r}
p6 = 273/390
(p6-0.75)/sqrt(0.75*0.25/390)
```
a) The critical region for  $\alpha = 0.05$ is:
```{r}
-qnorm(0.95)
```
i.e: $p\leq-1.644854$
Since value of the test statistic is in the critical region, we reject $H_0$ at $\alpha = 0.05$

b) The critical region for  $\alpha = 0.1$ is:
```{r}
-qnorm(0.99)
```
Since value of the test statistic is not the critical region, we fail to reject $H_0$ at $\alpha = 0.05$  
c)The p value is:
```{r}
pnorm(-2.280)
```

## Problem 8.3.7
a) The critical region is:
```{r}
qnorm(0.95)
```
i.e: $p\geq 1.644854$  
b) The value of the test statistic is:
```{r}
p7 = 550/1278
(p7 -0.4)/sqrt(0.4*0.6/1278)
```
Since the value of the test statistic falls into the critical region, we reject $H_0$ at $\alpha=0.05$ significance level

## Problem 8.3.8
a)  
$H_0$ is p = 0.14
$H_1$ is p > 0.14
b) The critical region is:
```{r}
qnorm(0.99)
```
i.e: $p\geq2.326348$  

c) The value of the test statistic is:
```{r}
p8 = 104/590
(p8-0.14)/sqrt(0.14*0.86/590)
```
Since the value of the test statistic is within the critical region, we reject $H_0$

## Problem 8.3.11
a)
The two-tailed critical region is:
```{r}
qnorm(0.975)
```
i.e: $p\leq - 1.959964$ or $p\geq  1.959964$  
The sketch of critical region (2 tailed):
```{r, out.width="300px", out.height="300px"}
xseq=seq(-4,4,.01)
densities=dnorm(xseq, 0,1)
plot(xseq, densities,xlab="", ylab="Density", type="l", main="PDF of Standard Normal")
```

b) The value of the test statistic is:
```{r}
p111 = 37/1000
p211 = 53/1000
p311 = (37+53)/2000
(p111-p211)/sqrt(p311*(1-p311)*(2/1000))
```
Thus, the value of the test statistic is outside the critical region and we reject $H_0$ at $\alpha = 0.05$ significance level

## Problem 8.3.14
a) The critical region is:
```{r}
qnorm(0.95)
```
i.e: $p\geq 1.644854$
b) The value of the test statistic is:
```{r}
p114 = 135/900
p214 = 77/700
p314 = (135+77)/(900+700)
(p114-p214)/sqrt(p314*(1-p314)*(1/900+1/700))
```
Since the value of the test statistic is in the critical region, we reject $H_0$  
c) The p value is:
```{r}
1-pnorm(2.341)
```