---
title: "Homework 8.1"
author: "Duong Ngo"
date: "10/16/2019"
output: pdf_document
header-includes: 
    - \usepackage{amsmath}
---

## Problem 8.1.2
a) The value of the test statistic is:
```{r}
(12.6-13)/(0.2/sqrt(25))
```
Since $-10<z_{0.025}$, we reject $H_0$  
b) The value of the test statistic is:
```{r}
(12.9-13)/(0.2/sqrt(25))
```
Since $-2.5<z_{0.025}$, we reject $H_0$  
c)  
In case a) the P value is:  
```{r}
pnorm(-10)
```
In case b) the P value is:  
```{r}
pnorm(-2.5)
```
## Problem 8.1.3
a) The value of the test statistic is:  
$\frac{\bar{X}-170}{\sigma/\sqrt{n}}=\frac{\bar{X}-170}{2}$  
Plotting the value showing the critical region of $\alpha=0.05$  
```{r}
xseq=seq(-4,4,.01)
densities=dnorm(xseq, 0,1)
plot(xseq, densities,xlab="", ylab="Density", type="l", main="PDF of Standard Normal")
```
b) The sample mean is:
```{r}
d8113 = read.table('8_1-03.txt')
m8113 = mean(d8113[,1])
m8113
```
The value of the test statistic is:
```{r}
(m8113-170)/2
```
Since $1.26<1.645$, we do not reject $H_{0}$
c) The p value is:
```{r}
1-pnorm(1.26)
```
## Problem 8.1.4
a) In case the variance is unknown, the value of the test statistic is:  
$\frac{\bar{X}-7.5}{S/\sqrt{10}}$
Since we have:
```{r}
qt(0.025,9)
```
The critical region at $\alpha=0.05$ for two-sided alternative hypothesis is:   
$t\geq\mid2.262157\mid)$
Plotting the value showing the critical region of $\alpha=0.05$  
```{r}
xseq=seq(-4,4,.01)
densities=dnorm(xseq, 0,1)
plot(xseq, densities,xlab="", ylab="Density", type="l", main="PDF of Standard Normal")
```
b) The sample mean and standard deviation is:
```{r}
d8114 = read.table('8_1-04.txt')
m8114 = mean(d8114[,1])
sd8114 = sd(d8114[,1])
```
Thus the value of the test statistic is:
```{r}
(m8114-7.5)/(sd8114/sqrt(10))
```
Since the value of the test statistic is within the critical region, we do not reject $H_0$  
c) The 95% confidence interval of the mean is:
```{r}
c(m8114+qt(0.025, 9)*sd8114/sqrt(10), m8114-qt(0.025, 9)*sd8114/sqrt(10))
```
Thus 7.5 is contained within the 95% confidence interval of the mean  
## Problem 8.1.6
a) The null hypothesis is $\mu=3.4$
b) The alternative hypothesis is $\mu>3.4$
c) The test statistic is:
$\frac{\bar{X}-3.4}{S/3}$
d) We have:
```{r}
qt(0.95, 8)
```
Thus one-sided critical region for $\alpha=0.05$ is:  
$t\geq1.859548$  
Plotting the value showing the critical region of $\alpha=0.05$    
```{r}
xseq=seq(-4,4,.01)
densities=dnorm(xseq, 0,1)
plot(xseq, densities,xlab="", ylab="Density", type="l", main="PDF of Standard Normal")
```
e) The sample mean and sample standard deviation is:
```{r}
d8116 = read.table('8_1-06.txt')
m8116 = mean(d8116[,1])
sd8116 = sd(d8116[,1])
```
Thus the value of the test statistic is:
```{r}
(m8116-3.4)/(sd8116/3)
```
f) Since 2.8 is in the critical region of the test statistic, we reject $H_{0}$
g) The p value is
```{r}
1-pt(2.8, 8)
```
## Problem 8.1.9
a) The sample mean and variance is:
```{r}
d8119 = read.table('8_1-09.txt')
m8119 = mean(d8119[,1])
sd8119 =sd(d8119[,1])
```
Thus the value of the test statistic is:
```{r}
(m8119-15.7)/(sd8119/sqrt(33))
```
The p value for the test is:
```{r}
pt(-4.599006, 32)
```
b) Since the p value is in the critical region, we reject $H_{0}$
c) The upper bound of one-sided confidence interval for the mean is
```{r}
m8119+qt(0.98,32)*sd8119/sqrt(33)
```
## Problem 8.1.11
The critical region value is:
```{r}
qt(0.95, 9)
```
The mean and the standard deviation of d is:
```{r}
d8111 = read.table('8_1-11.txt')
m8111 = mean(d8111[,1]-d8111[,2])
sd8111 = sd(d8111[,1]-d8111[,2])
```
The value of the test statistic is:
```{r}
m8111/(sd8111/sqrt(10))
```
Since the value of the test statistic is within the critical region, we do not reject $H_0$
## Problem 8.1.13  
a)  
The critical region value is:
```{r}
qt(0.95, 19)
```
Plotting the value showing the critical region of $\alpha=0.05$  
```{r}
xseq=seq(-4,4,.01)
densities=dnorm(xseq, 0,1)
plot(xseq, densities,xlab="", ylab="Density", type="l", main="PDF of Standard Normal")
```
From the plot, we see the critical region is $t\leq 1.729133$  
b) The sample mean and standard deviation of the data is:
```{r}
d81113 = read.table('8_1-13.txt')
m81113 = mean(d81113[,1]-d81113[,2])
sd81113 = sd(d81113[,1]-d81113[,2])
```
The value of the test statistic is:
```{r}
m81113/(sd81113/sqrt(20))
```
Since the value of the test statistic is outside of the critical region, we reject $H_0$  
c) The critical region at $\alpha = 0.01$ is:  
```{r}
qt(0.01, 19)
```
Since the test statistic is within the critical region, we do not reject $H_0$ when $\alpha = 0.01$  
d) The p value is:
```{r}
1- pt(2.248709, 19)
```