---
title: "R Project 3"
author: "Duong Ngo"
date: "11/2/2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Creating the required sample size:  
Sample size of about a dozen with population variance 1 (Sample 1):
```{r}
dozensamplesize = rnorm(12, 1, 1)
v1 = var(dozensamplesize)
n1 = 12
v1
```
Sample size between 30 and 40 with population variance 1.4 (Sample 2):
```{r}
magicsamplesize = rnorm(35, 1, 1.4)
v2 = var(magicsamplesize)
n2 = 35
v2
```
Sample siZe between 100 and 300 with population variance 1.8 (Sample 3):
```{r}
largesamplesize = rnorm (200, 1, 1.8)
v3 = var(largesamplesize)
n3 = 200
v3
```
Sample size between 1000 and 2000 with population variance 2.2 (Sample 4):
```{r}
giganticsamplesize = rnorm(2000, 1, 2.2)
v4 = var(giganticsamplesize)
n4 = 2000
v4
```

Mixtured sample (Sample 5):
```{r}
mixsampliesize = c(dozensamplesize[1:10], magicsamplesize[1:50], largesamplesize[1:100], giganticsamplesize[1:200])
v5 = var(mixsampliesize, na.rm=TRUE)
n5 = 360
v5
```
Function for variance test:
```{r}
vartest = function(alpha, df1, df2, ratio)
    1-pf(qf(1-alpha, df1, df2)*ratio,df1,df2)
```
Result when comparing a very small sample size (a dozen) with larger sample size  
a)Comparing Sample 1 and Sample 2:
```{r}
r12 = var(dozensamplesize)/var(magicsamplesize)
vartest(0.01, n1-1, n2-1, r12)
vartest(0.025, n1-1, n2-1, r12)
vartest(0.05, n1-1, n2-1, r12)
vartest(0.1, n1-1, n2-1, r12)
vartest(0.4, n1-1, n2-1, r12)
```
Conclusion: When comparing the variance of a very small sample size with another variance, the power function only return acceptable $1-\beta$ when given $\alpha$ error 0.4 (which is useless)
Comparing sample 1 and sample 3:
```{r}
r13 = var(dozensamplesize)/var(giganticsamplesize)
vartest(0.01, n1-1, n3-1, r13)
vartest(0.025, n1-1, n3-1, r13)
vartest(0.05, n1-1, n3-1, r13)
vartest(0.1, n1-1, n3-1, r13)
```
Major improvement when improve the second sample size from 35 to 200. Generating acceptable power right when $\alpha=0.01$  
Comparing sample 1 and sample 4:
```{r}
r14 = var(dozensamplesize)/var(giganticsamplesize)
vartest(0.025, n1-1, n4-1, r14)
```
Thus, needless to say when the second sample size is gigantic
Comparing sample 4 and sample 5:




