---
title: "R Project 2"
author: "Duong Ngo"
date: "10/8/2019"
output: pdf_document
---

# Confidence interval for p
Let the n value be 100
Let the Y value be $100*0.16 = 16$  
Method 1: Using equation 7.3.2:
```{r}
P1 = 0.16
cbind(P1-qnorm(0.95)*sqrt((P1*(1-P1))/100), P1+qnorm(0.95)*sqrt((P1*(1-P1))/100))
```
Method 2: Using equation 7.3.4:
```{r}
n1 = qnorm(.95)
cbind((P1+n1^2/(2*100)-n1*sqrt((P1-P1^2)/100+n1^2/(4*100^2)))/(1+(n1^2/100)),(P1+n1^2/(2*100)+n1*sqrt((P1-P1^2)/100+n1^2/(4*100^2)))/(1+(n1^2/100)))
```   
Method 3: Using equation 7.3.5:
```{r}
ep12 = (16+2)/(100+4)
cbind(ep12-qnorm(.95)*sqrt((ep12-ep12^2)/(100+4)),ep12+qnorm(.95)*sqrt((ep12-ep12^2)/(100+4)))
```

# Distribution-free confidence interval for percentile

### Ia) Finding $\pi_{50}$ for a sample size of 3000
Let $a$ be the hypothetical sample size of 3000 drawn from a population of exponential distribution with $\alpha = 0.22$
```{r}
a = rexp(3000, .22)
sorteda = sort(a)
```
Using the first method (Dr. Schweitzer Power Point Function), the point of order statistics for the 90% confidence interval of a is:
```{r}
cimedian = function(n, conf.level)
{i = 1
while((pbinom(n-i, n , .5) - pbinom(i-1, n , .5))>conf.level){i = i+1}
c(i-1,  n+1- (i-1), pbinom(n-(i-1), n, .5)- pbinom((i-1)-1, n, .5))}
cimedian(3000, .90)
```
Thus, the actual 90% confidence interval for $a$ using the first method is:
```{r}
c(sorteda[1456],sorteda[1547])
```

On the other hand, we can approximate for the confidence interval of $a$ as follow:  
First we find the point estimate for $\pi_{50}$
```{r}
pea = 0.5*3001
```
The 90% confidence interval for $a$ in term of order statistic is:
```{r}
c(floor(pea - qnorm(.95)*sqrt(0.5*0.5*3000)), ceiling(pea + qnorm(.95)*sqrt(0.5*0.5*3000)))
```
Thus, the exact 90% confidence interval for $a$ using the second method is:
```{r}
c(sorteda[1455], sorteda[1546])
```
### Ib) Finding $\pi_{50}$ for a sample size of 300

Let $b$ be the first 300 sample in the ordered statistic of $a$
```{r}
b = sorteda[1:300]
```
Using the first method (Dr. Schweitzer Power Point Function), the point of order statistics for the 90% confidence interval of b is:
```{r}
cimedian(300, .90)
```
Thus, the actual 90% confidence interval for $b$ using the first method is:
```{r}
c(b[137], b[166])
```

On the other hand, we can approximate for the confidence interval of $b$ as follow:  
First we find the point estimate for $\pi_{50}$
```{r}
peb = 0.5*301
```
The 90% confidence interval for $b$ in term of order statistic is:
```{r}
c(floor(peb - qnorm(.95)*sqrt(0.5*0.5*300)), ceiling(peb + qnorm(.95)*sqrt(0.5*0.5*300)))
```
Thus, the actual 90% confidence interval for $b$ using the second method is:
```{r}
c(b[137], b[166])
```
### Ic) Finding $\pi_{50}$ for a sample size of 30

Let $c$ be the first 300 sample in the ordered statistic of $a$
```{r}
c = sorteda[1:30]
```
Using the first method (Dr. Schweitzer Power Point Function), the point of order statistics for the 90% confidence interval of c is:
```{r}
cimedian(30, .90)
```
Thus, the actual 90% confidence interval for $b$ using the first method is:
```{r}
c(b[12], b[21])
```

On the other hand, we can approximate for the confidence interval of $b$ as follow:  
First we find the point estimate for $\pi_{50}$
```{r}
peb = 0.5*31
```
The 90% confidence interval for $b$ in term of order statistic is:
```{r}
c(floor(peb - qnorm(.95)*sqrt(0.5*0.5*30)), ceiling(peb + qnorm(.95)*sqrt(0.5*0.5*30)))
```
Thus, the actual 90% confidence interval for $b$ using the second method is:
```{r}
c(c[11], c[22])
```
### II) Other misc. calculation in part (3)
##### a) 90% confidence interval for 10 percentile of order statistic:
Function for computation of order statistic 
```{r}
orderstatpercentile = function(p, n, conf.level)
{ 
  output= c(floor(p*(n+1) - qnorm(1-((1-conf.level)/2))*sqrt(p*(1-p)*n)), ceiling(p*(n+1) + qnorm(1-((1-conf.level)/2))*sqrt(p*(1-p)*n)))
return(output)
}
```
90% Confidence interval of 10 percentile order statistic for sample size of 30, 300, and 3000
```{r}
orderstatpercentile(0.1, 30, 0.9)
orderstatpercentile(0.1, 300, 0.9)
orderstatpercentile(0.1, 3000, 0.9)
```
Thus, the exact probability associated with these interval are:
```{r}
pbinom(6, 30, 0.1) - pbinom(0, 30, 0.1)
pbinom(39, 300, 0.1) - pbinom(21, 300, 0.1)
pbinom(328, 3000, 0.1) - pbinom(273, 3000, 0.1)
```
Hence, the actual 10 percentile 90% confidence interval when applied to the generated sample are respectively:
```{r}
c(c[1],c[7])
c(b[22],b[40])
c(a[274],a[328])
```

##### b) 90% confidence interval for 25 percentile of order statistic:

90% Confidence interval of 25 percentile order statistic for sample size of 30, 300, and 3000
```{r}
orderstatpercentile(0.25, 30, 0.9)
orderstatpercentile(0.25, 300, 0.9)
orderstatpercentile(0.25, 3000, 0.9)
```
Thus, the exact probability associated with these interval are:
```{r}
pbinom(12, 30, 0.25) - pbinom(3, 30, 0.25)
pbinom(88, 300, 0.25) - pbinom(62, 300, 0.25)
pbinom(790, 3000, 0.25) - pbinom(711, 3000, 0.25)
```
Hence, the actual 25 percentile 90% confidence interval when applied to the generated sample are respectively:
```{r}
c(c[4],c[13])
c(b[63],b[89])
c(a[712],a[791])
```
##### c) 90% confidence interval for 75 percentile of order statistic:

90% Confidence interval of 75 percentile order statistic for sample size of 30, 300, and 3000
```{r}
orderstatpercentile(0.75, 30, 0.9)
orderstatpercentile(0.75, 300, 0.9)
orderstatpercentile(0.75, 3000, 0.9)
```
Thus, the exact probability associated with these interval are:
```{r}
pbinom(28, 30, 0.75) - pbinom(19, 30, 0.75)
pbinom(239, 300, 0.75) - pbinom(213, 300, 0.75)
pbinom(2290, 3000, 0.75) - pbinom(2211, 3000, 0.75)
```
Hence, their actual 75 percentile 90% confidence interval are respectively:
```{r}
c(c[4],c[13])
c(b[63],b[89])
c(a[712],a[791])
```